---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: This is a toy package created for expository purposes.**

# toypackageWZ

<!-- badges: start -->
<!-- badges: end -->

The goal of `toypackageWZ` is to provide convenience functions for some common tasks.

## Installation

You can install the development version of `toypackageWZ` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
# install.packages("devtools")
devtools::install_github("willzatkowski/toypackageWZ")
```

## Examples

This is a basic example which shows you how to solve a common problem:

```{r example}
library(toypackageWZ)
```

#### strsplit1 example

```{r}
first_subject_words <- toy_data$recalled_words[1]
strsplit1(first_subject_words, split = ", ")
```

#### min_max_scale example

```{r}
min_max_scale(toy_data$test_score)
```

#### theme_academic example

```{r, fig.align='center'}
library(ggplot2)
ggplot(toy_data, aes(x = reaction_time, y = test_score)) +
geom_point(size = 4, color = "steelblue") +
labs(title = "Faster Reaction Times Correlate with Higher Scores",
x = "Reaction Time (seconds)", y = "Scaled Test Score (0 to 1)") +
theme_academic(base_size = 14)
```
